### 2023-07-12 calculus.tex
Writing, cleanup

Programmers often work with program states that are syntactically well-formed but not well-typed.
\Cref{fig:calculus-examples} shows common type errors as they appear in the Hazel programming
environment. 
% For example, a simple error that may occur is the use of an free variable (\cref{fig:calculus-examples-free}).
% As in \cref{fig:calculus-examples-unbound}, the editor indicates that the usage of an free $y$ is
% invalid by highlighting it in red.

>>>>

To begin to motivate the development of this section, consider \cref{fig:calculus-examples}, which
shows common type errors as they appear in the Hazel programming environment. These programs are
syntactically well-formed but ill-typed.
% For example, a simple error that may occur is the use of an free variable (\cref{fig:calculus-examples-free}).
% As in \cref{fig:calculus-examples-unbound}, the editor indicates that the usage of an free $y$ is
% invalid by highlighting it in red.

### 2023-07-12 polymorphism.tex
Clean up some writing in section 2
Writing, cleanup

\subsection{Parametric Polymorphism}
\label{sec:calculus-polymorphism}

@@

The case studies above demonstrate that the framework of the marked lambda calculus is suitable to support a variety of extensions to richer judgmental structures.
We hope that this spurs language designers to design marked variants of other calculi, following the recipe we have demonstrated.
% TODO explicitly give recipe.

We leave as future work the task of defining a marked version of even more elaborate bidirectional type systems, e.g. \citet{dunfield2013complete}'s rather substantial formulation of implicit type application in a bidirectional setting (which would have to handle, for example, the situation where no implicit argument can be resolved).

>>>>

\subsection{Parametric Polymorphism and Richer Judgmental Structures}
\label{sec:calculus-polymorphism}

@@

The case studies above demonstrate that the framework of the marked lambda calculus is suitable to support a variety of extensions to richer judgmental structures.
We hope that this spurs language designers to design marked variants of other calculi, following the
recipe we have demonstrated: starting with a gradual, bidirectional type system, by considering each
possible failure case, one may systematically derive the necessary error marks and marking rules.

We leave as future work the task of defining marked versions of even more elaborate bidirectional
type systems, e.g. \citet{dunfield2013complete}'s rather substantial formulation of implicit type
application in a bidirectional setting (which would have to handle, for example, the situation where
no implicit argument can be resolved).
